Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-09-10 journal paper/journal_main.tex
Reverted the section title for app/bg.
Inserted some \newpage macro.
one small tweak to intro and use newer econometrica bst
Minor edits in the title note.

\title{\vspace{-12mm}Competing Bandits:\\
The Perils of Exploration under Competition%
\thanks{This is a merged and final version of two conference papers,
\citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19},
with a unified and streamlined presentation and expanded background materials. All theoretical results are from \citet{CompetingBandits-itcs18}, and all experiments are from \citet{CompetingBandits-ec19}. Appendices~\ref{app:bg},\ref{app:examples} are completely new compared to the conference versions. We would like to thank Yeon-Koo Che, Glen Weyl, Sven Rady, and seminar participants at Columbia, ACM Economics and Computation, and Innovations in Theoretical Computer Science for helpful comments and conversations. All errors are our own.} }
% \textit{Competing Bandits: Learning under Competition}, at Innovations in Theoretical Computer Science 2018, and \textit{The Perils of Exploration under Competition: A Computational Modeling Approach}, at ACM Economics and Computation 2019.}}

@@

\section{Numerical simulations: the \ExptsModel}
\label{sec:sim}
%\label{sec:sim_details}

@@

\bibliographystyle{econometrica}
%\begin{small}
\bibliography{bib-abbrv,bib-ML,refs,bib-bandits,bib-AGT,bib-slivkins, bib-random}
%\end{small}

@@

\section{Background on multi-armed bandits}
\label{app:bg}
%\label{sec:related-classes}
\subfile{content/sec-bg}

>>>>

\title{\vspace{-12mm}Competing Bandits:\\
The Perils of Exploration under Competition%
\thanks{This is a merged and final version of two conference papers,
\citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19},
with a unified and streamlined presentation and expanded related work and background materials. All theoretical results are from \citet{CompetingBandits-itcs18}, and all experiments are from \citet{CompetingBandits-ec19}. Appendices~\ref{app:bg},\ref{app:examples} are completely new compared to the conference versions. We would like to thank Ian Ball, Yeon-Koo Che, Glen Weyl and Sven Rady, as well as seminar participants at Columbia and conference participants at Innovations in Theoretical Computer Science 2018 and ACM Economics and Computation 2019, for helpful comments and conversations. All errors are our own.} }
% \textit{Competing Bandits: Learning under Competition}, at Innovations in Theoretical Computer Science 2018, and \textit{The Perils of Exploration under Competition: A Computational Modeling Approach}, at ACM Economics and Computation 2019.}}

@@

\newpage
\section{Numerical simulations: the \ExptsModel}
\label{sec:sim}
%\label{sec:sim_details}

@@

\bibliographystyle{ecta.bst}
%\begin{small}
\bibliography{bib-abbrv,bib-ML,refs,bib-bandits,bib-AGT,bib-slivkins, bib-random}
%\end{small}

@@

\section{Background for non-specialists: \\multi-armed bandits}
\label{app:bg}
%\label{sec:related-classes}
\subfile{content/sec-bg}

\newpage
